### 2019-03-27 _publications/jors/paper.tex
Remove new para before and after itemize list

The workflow for uploading benchmark results relies on third party
tools using the following steps, illustrated in
Figure~\ref{fig:pfhub_website}.

\begin{itemize}
  \item The users are first required to upload simulation outputs to
    an archival resource (\emph{e.g.},
    Figshare~\cite{figshare}~\footnote{Certain commercial equipment,
      instruments, or materials (or suppliers, or software, ...) are
      identified in this paper to foster understanding. Such
      identification does not imply recommendation or endorsement by
      the National Institute of Standards and Technology, nor does it
      imply that the materials or equipment identified are necessarily
      the best available for the purpose.\label{disclaimer}})
    configured with permissive cross-origin resource sharing (CORS).
  \item The metadata summarizing each simulation is entered into a
    form on the website, including relevant details such as memory
    usage, run time and links to the data archived in the first step.
  \item Upon submission, the Staticman app~\cite{staticman} submits
    the entered metadata as a GitHub pull request to the PFHub GitHub
    repository.  The metadata is stored in a YAML file with a unique
    path in the repository.
  \item Travis CI~\cite{travis} performs linting on the submission and
    then launches a temporary version of the proposed website using
    Surge~\cite{surge}. The PFHub admins can then examine the new
    submission and further changes can be made if necessary.
  \item Once review has been completed to the satisfaction of both the
    uploading scientist and the website maintainers, the pull request
    is merged and served to the World Wide Web using a hosting service
    compatible with GitHub Pages.
\end{itemize}

A combination of Jekyll templates and Coffeescript are used to access
and download the data links in the submitted YAML files and then
display the data in interactive plots on the website. The interactive
plots are displayed using the Plotly JavaScript Graphing
Library~\cite{plotly} as it provides a programmable interface and
requires minimal configuration.

>>>>

The workflow for uploading benchmark results relies on third party
tools using the following steps, illustrated in
Figure~\ref{fig:pfhub_website}.
\begin{itemize}
  \item The users are first required to upload simulation outputs to
    an archival resource (\emph{e.g.},
    Figshare~\cite{figshare}~\footnote{Certain commercial equipment,
      instruments, or materials (or suppliers, or software, ...) are
      identified in this paper to foster understanding. Such
      identification does not imply recommendation or endorsement by
      the National Institute of Standards and Technology, nor does it
      imply that the materials or equipment identified are necessarily
      the best available for the purpose.\label{disclaimer}})
    configured with permissive cross-origin resource sharing (CORS).
  \item The metadata summarizing each simulation is entered into a
    form on the website, including relevant details such as memory
    usage, run time and links to the data archived in the first step.
  \item Upon submission, the Staticman app~\cite{staticman} submits
    the entered metadata as a GitHub pull request to the PFHub GitHub
    repository.  The metadata is stored in a YAML file with a unique
    path in the repository.
  \item Travis CI~\cite{travis} performs linting on the submission and
    then launches a temporary version of the proposed website using
    Surge~\cite{surge}. The PFHub admins can then examine the new
    submission and further changes can be made if necessary.
  \item Once review has been completed to the satisfaction of both the
    uploading scientist and the website maintainers, the pull request
    is merged and served to the World Wide Web using a hosting service
    compatible with GitHub Pages.
\end{itemize}
A combination of Jekyll templates and Coffeescript are used to access
and download the data links in the submitted YAML files and then
display the data in interactive plots on the website. The interactive
plots are displayed using the Plotly JavaScript Graphing
Library~\cite{plotly} as it provides a programmable interface and
requires minimal configuration.
